Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-10 thirdPaper/draft/typeConeAssociahedra.tex
proof of Prop 2.41

We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, so does its normal fan.
Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.

@@

Gentle associahedra were constructed by Y.~Palu, V.~Pilaud and P.-G.~Plamondon~\cite{PaluPilaudPlamondon-nonkissing} in the context of support $\tau$-tilting for gentle algebras.
For a given $\tau$-tilting finite gentle quiver~$\quiver$ (defined in the next section), the $\quiver$-associahedron~$\Asso[\quiver]$ is a simple polytope which encodes certain representations of~$\quiver$ and their $\tau$-tilting relations.
Combinatorially, the $\quiver$-associahedron is a polytopal realization of the non-kissing complex of~$\quiver$, defined as the simplicial complex of all collections of walks on the blossoming quiver~$\quiver\blossom$ which are pairwise non-kissing.
The non-kissing complex encompasses two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
These two families naturally extend the classical associahedron, obtained from a line quiver.
Non-kissing complexes are geometrically realized by polytopes called gentle associahedra, whose normal fan is called the non-kissing fan: its rays correspond to walks in the quiver and its cones are generated by the non-kissing walks.
In this section, we describe the type cone of the non-kissing fan of a quiver~$\quiver$ with no self-kissing walks.

@@

We present the definitions and properties of the non-kissing complex of a gentle quiver, following the presentation of~\cite{PaluPilaudPlamondon-nonkissing}.

@@

\para{Non-kissing complex}
%
Let~$\omega$ and~$\omega'$ be two undirected walks on~$\quiver$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$.
In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
%See \fref{fig:kissing}.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
For example, \cref{fig:exmNonkissing}\,(middle) shows three walks that are pairwise kissing, and the orange walk is self-kissing (at its self-intersection).
We say that a walk is \defn{proper} if it is not straight nor self-kissing.
We denote by~$\properWalks$ the set of all proper walks of~$\quiver$.

%\begin{figure}[h]
%	\capstart
%	\centerline{\includegraphics[scale=1]{kissing}}
%	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
%	\label{fig:kissing}
%\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection}}
	\caption{A gentle grid quiver (left), a gentle dissection quiver (middle left), and a path quiver which is both the gentle grid quiver of a ribbon (middle right) and the dissection quiver of a triangulation (right). Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:dissectionGridQuivers}
\end{figure}

@@

To define the other family of vectors, we need to recall the notion of distinguished substring of a walk defined in~\cite[Def.~2.25]{PaluPilaudPlamondon-nonkissing}.
Consider an arrow~$\alpha \in Q_1$ contained in two distinct walks~$\omega, \omega'$ of a non-kissing facet~$F \in \NKC$, and let~$\sigma$ denote the common substring of~$\omega$ and~$\omega'$.
We write~$\omega \prec_\alpha \omega'$ if $\omega$ enters and/or exits~$\sigma$ with arrows in the direction pointed by~$\alpha$, while $\omega'$ enters and/or exits~$\sigma$ with arrows in the direction opposite to~$\alpha$.
The \defn{distinguished walk} of the non-kissing facet~$F \in \NKC$ at the arrow~$\alpha$ is the maximum walk of~$F$ for~$\prec_\alpha$.
The \defn{distinguished arrows} of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ are the arrow where~$\omega$ is the distinguished walk.
It is shown in~\cite[Prop.~2.28]{PaluPilaudPlamondon-nonkissing} that each bending walk in a non-kissing facet has precisely two distinguished arrows, pointing in opposite directions.
For example, we have marked in \cref{fig:exmNonkissing}\,(right) the two distinguished arrows on each walk by triple arrows.
The \defn{distinguished substring}~$\distinguishedString{\omega}{F}$ of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ is the substring located between its two distinguished arrows.
We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished string of a walk in a non-kissing facet, and we denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.

@@

\para{Non-kissing fan and gentle associahedron}
%
The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex complex.
Examples are illustrated in \cref{fig:nonkissingFans}.

@@

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.45]{nonkissingFans}}
	\caption{Two non-kissing fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:nonkissingFans}
\end{figure}

@@

\para{Flips in the non-kissing fan}
%
Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}), we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
The following statement is partially proved in~\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}.

\begin{proposition}
\label{prop:exchangeablePairsNKC}
Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then
\begin{enumerate}[(i)]
\item For any non-kissing facet~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, there exists a unique maximal common substring~$\sigma$ of~$\omega$ and~$\omega'$ that decomposes~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$ such that the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
\item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
\[
\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
\]
In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
\end{enumerate}
\end{proposition}

@@

\begin{example}
\label{exm:typeConeNKC}
Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).

@@

\noindent
The type cone of the right fan of \cref{fig:nonkissingFans} lives in~$\R^{11}$ and has a linearity space of dimension~$3$.
It has $9$ facet-defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right).
In particular, it is not simplicial.

@@

\begin{figure}

@@

\begin{proof}
We just need to prove that there exists a ridge~$R$ of~$\NKC$ containing both~$\hc{\sigma}$ and~$\ch{\sigma}$ and such that~$R \cup \{\cc{\sigma}\}$ and~$R \cup \{\hh{\sigma}\}$ are adjacent facets of~$\NKC$.

\vincent{TODO}
\end{proof}

@@

\vincent{Describe the rays of the type cone. They are the Minkowski basis.}

@@

\subsection{Graphical nested complexes and graph associahedra}
\label{subsec:typeConeGA}

>>>>

\enlargethispage{.1cm}
We now focus on the normal fan~$\gvectorFan[n]$ of~$\Asso[n]$.
Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, so does its normal fan.
Let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} x_\ell = 0}$ and~$\pi : \R^{n+1} \to \HH$ denote the orthogonal projection.
The following fans are illustrated in \cref{fig:lodayFans} in dimension~$2$ and~$3$.

@@

\enlargethispage{-.4cm}
Gentle associahedra were constructed by Y.~Palu, V.~Pilaud and P.-G.~Plamondon~\cite{PaluPilaudPlamondon-nonkissing} in the context of support $\tau$-tilting for gentle algebras.
For a given $\tau$-tilting finite gentle quiver~$\quiver$ (defined in the next section), the $\quiver$-associahedron~$\Asso[\quiver]$ is a simple polytope which encodes certain representations of~$\quiver$ and their $\tau$-tilting relations.
Combinatorially, the $\quiver$-associahedron is a polytopal realization of the non-kissing complex of~$\quiver$, defined as the simplicial complex of all collections of walks on the blossoming quiver~$\quiver\blossom$ which are pairwise non-kissing.
The non-kissing complex encompasses two families of simplicial complexes studied independently in the literature: on the one hand the grid associahedra introduced by T.~K.~Petersen, P.~Pylyavskyy and D.~Speyer in~\cite{PetersenPylyavskyySpeyer} for a staircase shape, studied by F.~Santos, C.~Stump and V.~Welker~\cite{SantosStumpWelker} for rectangular shapes, and extended by T.~McConville in~\cite{McConville} for arbitrary grid shapes; and on the other hand the Stokes polytopes and accordion associahedra studied by Y.~Baryshnikov~\cite{Baryshnikov}, F.~Chapoton~\cite{Chapoton-quadrangulations}, A.~Garver and T.~McConville~\cite{GarverMcConville} and T.~Manneville and V.~Pilaud~\cite{MannevillePilaud-accordion}.
These two families naturally extend the classical associahedron, obtained from a line quiver.
Non-kissing complexes are geometrically realized by polytopes called gentle associahedra, whose normal fan is called the non-kissing fan: its rays correspond to walks in the quiver and its cones are generated by the non-kissing walks.
In this section, we describe the type cone of the non-kissing fan of a quiver~$\quiver$ with no self-kissing walks.

@@

We present the definitions and properties of the non-kissing complex of a gentle quiver, following the presentation of~\cite{PaluPilaudPlamondon-nonkissing}.
See also~\cite{BrustleDouvilleMousavandThomasYildirim} for an alternative presentation.

@@

\para{Non-kissing complex}
%
Let~$\omega$ and~$\omega'$ be two undirected walks on~$\quiver$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if ${\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega')} \ne \varnothing$.
In other words, $\omega$ and~$\omega'$ share a common substring~$\sigma$, and both arrows of~$\omega$ (resp.~of~$\omega'$) not in~$\sigma$ are outgoing (resp.~incoming) at the endpoints of~$\sigma$.
See \cref{fig:kissingCrossing} for a schematic representation and \cref{fig:exmNonkissing}\,(middle) where the three walks are pairwise kissing.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where the common finite substring is reduced to a vertex~$a$, that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
For example, the orange walk in \cref{fig:exmNonkissing}\,(middle) is self-kissing (at its self-intersection).
We say that a walk is \defn{proper} if it is not straight nor self-kissing.
We denote by~$\properWalks$ the set of all proper walks of~$\quiver$.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissingCrossing}}
	\caption{A schematic representation of kissing and non-kissing walks. The walks $\omega$ and~$\omega'$ kiss (left) while the walks~$\mu$ and~$\nu$ share a common substring but do not kiss (right). Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:kissingCrossing}
\end{figure}

@@

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.35]{gridQuiver} \quad \includegraphics[scale=.8]{dissectionQuiver} \quad \includegraphics[scale=1.2]{bijectionAssociahedronGrid} \quad \includegraphics[scale=1.2]{bijectionAssociahedronDissection}}
	\caption{A gentle grid quiver (left), a gentle dissection quiver (middle left), and a path quiver which is both the gentle grid quiver of a ribbon (middle right) and the dissection quiver of a triangulation (right). Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:dissectionGridQuivers}
\end{figure}

@@

To define the other family of vectors, we need to recall the notion of distinguished substring of a walk defined in~\cite[Def.~2.25]{PaluPilaudPlamondon-nonkissing}.
Consider an arrow~$\alpha \in Q_1$ contained in two distinct walks~$\omega, \omega'$ of a non-kissing facet~$F \in \NKC$, and let~$\sigma$ denote the common substring of~$\omega$ and~$\omega'$.
We write~$\omega \prec_\alpha \omega'$ if $\omega$ enters and/or exits~$\sigma$ with arrows in the direction pointed by~$\alpha$, while $\omega'$ enters and/or exits~$\sigma$ with arrows in the direction opposite to~$\alpha$.
For example, in \cref{fig:kissingCrossing}, we have~$\mu \prec_\gamma \nu$ but~$\nu \prec_\delta \mu$.
The \defn{distinguished walk} of the non-kissing facet~$F \in \NKC$ at the arrow~$\alpha$ is the maximum walk of~$F$ for~$\prec_\alpha$.
The \defn{distinguished arrows} of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ are the arrow where~$\omega$ is the distinguished walk.
It is shown in~\cite[Prop.~2.28]{PaluPilaudPlamondon-nonkissing} that each bending walk in a non-kissing facet has precisely two distinguished arrows, pointing in opposite directions.
For example, we have marked in \cref{fig:exmNonkissing}\,(right) the two distinguished arrows on each walk by triple arrows.
The \defn{distinguished substring}~$\distinguishedString{\omega}{F}$ of the walk~$\omega$ in the non-kissing facet~$F \in \NKC$ is the substring located between its two distinguished arrows.
We say that a string~$\sigma$ is \defn{distinguishable} if it is the distinguished string of a walk in a non-kissing facet, and we denote by~$\distinguishableStrings$ the set of distinguishable strings of~$\quiver$.

@@

\para{Non-kissing fan and gentle associahedron}
%
\enlargethispage{.2cm}
The $\b{g}$-vectors support a complete simplicial fan realization of the non-kissing complex complex.
Examples are illustrated in \cref{fig:nonkissingFans}.

@@

\begin{figure}[b]
	\capstart
	\centerline{\includegraphics[scale=.45]{nonkissingFans}}
	\caption{Two non-kissing fans. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:nonkissingFans}
\end{figure}

@@

\para{Flips in the non-kissing fan}
%
\enlargethispage{-.4cm}
Although we lack a characterization of the exchangeable pairs of the non-kissing complex (see \cref{rem:exchangeablePairsNKC}), we can still describe the linear dependence among the $\b{g}$-vectors involved in a flip.
The following statement is partially proved in~\cite[Thm.~4.17]{PaluPilaudPlamondon-nonkissing}.
The notations are illustrated in \cref{fig:flip}.

\begin{proposition}
\label{prop:exchangeablePairsNKC}
Let~$\omega, \omega'$ be two exchangeable walks on~$\quiver$. Then
\begin{enumerate}[(i)]
\item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$. Moreover, if we decompose~$\omega = \rho \sigma \tau$ and~$\omega' = \rho' \sigma \tau'$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ actually depend on the exchangeable walks~$\omega$ and~$\omega'$, not on the adjacent non-kissing facet~$F $ and~$F'$.
\item Moreover, the linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
\[
\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
\]
In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
\end{enumerate}
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{flip}}
	\caption{A schematic representation of a flip. Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:flip}
\end{figure}
\end{proposition}

@@

\begin{example}
\label{exm:typeConeNKC}
\enlargethispage{.4cm}
Consider the non-kissing fans illustrated in \cref{fig:nonkissingFans}.
The type cone of the left fan of \cref{fig:nonkissingFans} lives in~$\R^9$ and has a linearity space of dimension~$3$.
It has $6$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:interestingExchangeablePairsNKC,prop:extremalExchangeablePairsNKC} and illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(left).

@@

\medskip
\noindent
The type cone of the right fan of \cref{fig:nonkissingFans} lives in~$\R^{11}$ and has a linearity space of dimension~$3$.
It has $9$ facet-defining inequalities (given below), which correspond to the flips illustrated in \cref{fig:labelFacetDefiningInequalititiesNKC}\,(right).
In particular, it is not simplicial.

@@

@@

\begin{proof}
We fix some notations similar to that of \cref{fig:flip}.
Let~$\omega \eqdef \cc{\sigma}$, $\omega' \eqdef \hh{\sigma}$, $\mu \eqdef \hc{\sigma}$ and~$\nu \eqdef \ch{\sigma}$.
%Let~$v,y$ be the two endpoints of~$\sigma$, and let~$u$ (resp.~$w$, resp.~$x$, resp.~$z$) be the only peak of~$\mu$ (resp.~deep of~$\mu$, resp.~peak of~$\nu$, resp.~deep of~$\nu$) that is not a substring of~$\sigma$.
%Finally, let~$\alpha = v \to w$, $\alpha' = u \to v$, $\beta = y \to z$ and $\beta' = x \to y$.
See \cref{fig:flip}.

Since~$\quiver$ is brick, these walks are not self-kissing by \cref{prop:noSelfKissing} and since they are bending, they are proper walks.
We want to show that there are non-kissing facets~$F, F'$ of the non-kissing complex~$\NKC$ containing both~$\mu$ and~$\nu$ and such that~$F \ssm \{\omega\} = F' \ssm \{\omega'\}$.

We first show that~$\mu$ and~$\nu$ are compatible.
Let~$\tau$ be a maximal common substring of~$\mu$ and~$\nu$.
If~$\sigma$ and~$\tau$ are not disjoint, then~$\sigma = \tau$ and $\mu$ and~$\nu$ are not kissing at~$\tau$.
We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.
We distinguish the different cases:
\begin{itemize}
\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ form a cycle in~$\quiver$. If~$\tau$ is reduced to a vertex, then we have a $2$-cycle. Otherwise, since~$\alpha\tau$ is a substring of~$\nu$ and~$\alpha'\tau$ is a substring of~$\nu$, the cycle~$\alpha \tau \alpha'$ contains a unique relation~$\alpha'\alpha$. This rules out this case under the assumption that~$\quiver$ is brick $2$-acyclic. The case when~$\tau$ appears after~$\sigma$ in both~$\mu$ and~$\nu$ is symmetric.
\item If~$\tau$ appears before~$\sigma$ in~$\mu$ and after~$\sigma$ in~$\nu$, then~$\omega$, $\mu$ and~$\nu$ finish at the same blossom so that~$\mu$ and~$\nu$ are not kissing at~$\tau$. The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is identical.
\end{itemize}
We conclude that~$\mu$ and~$\nu$ are non-kissing, which also implies that~$\{\mu, \nu, \omega\}$ and~$\{\mu, \nu, \omega'\}$ are non-kissing faces of~$\NKC$.
We can therefore consider a non-kissing facet~$F$ containing~$\{\mu, \nu, \omega\}$.

We claim that~$\omega$ is distinguished at~$\alpha$ and~$\beta$ in the facet~$F$, that~$\mu$ is distinguished at~$\alpha'$ and that~$\nu$ is distinguished at~$\beta'$.
Let us just prove that~$\mu$ is distinguished at~$\alpha'$, the other statements being similar.
Consider any walk~$\lambda$ of~$F$ containing~$\alpha'$, and let~$\tau$ be the maximal common substring of~$\omega$ and~$\lambda$.
Note that~$\omega$ has the outgoing arrow~$\alpha$ while~$\lambda$ has the incoming arrow~$\alpha'$ at one end of~$\tau$.
Since~$\omega$ and~$\lambda$ are compatible, it ensures that either~$\tau$ ends at a blossom, or $\lambda$ has an outgoing arrow at the other end of~$\tau$.
This shows that~$\lambda \prec_{\alpha'} \mu$ since $\lambda$ separates from~$\mu$ with an arrow in the same direction as~$\alpha'$.

Since this precisely coincides with the description of the flip in the non-kissing complex (see \cref{prop:exchangeablePairsNKC}\,(i) or \cite[Prop.~2.31]{PaluPilaudPlamondon-nonkissing} for an alternative presentation), we conclude that the flip of~$\omega$ in~$F$ creates a facet~$F'$ containing~$\omega'$.
Therefore, $\omega$ and~$\omega'$ are exchangeable with distinguished substring~$\sigma$.
\end{proof}

@@

@@

\newpage
\subsection{Graphical nested complexes and graph associahedra}
\label{subsec:typeConeGA}
